RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-31 manuscripts/manuscript.Rmd
Populating nexml in-memory objects section.

Instead of packaging the various components for a NeXML file at the
time of writing the file, the user can also create and iteratively
populate an in-memory R object representation of the NeXML document,
i.e., an object of type `nexml`. The methods to do this are `add_characters()`,
`add_trees()`, and `add_meta()`, for adding characters, trees, and
metadata, respectively. Each of these functions will automatically
create a new nexml object if not supplied with an existing one as the
last (optional) argument.

>>>>

Instead of packaging the various components for a NeXML file at the
time of writing the file, `RNeXML` also allows users to create and
iteratively populate an in-memory `nexml` object. The methods to do
this are `add_characters()`, `add_trees()`, and `add_meta()`, for
adding characters, trees, and metadata, respectively. Each of these
functions will automatically create a new nexml object if not supplied
with an existing one as the last (optional) argument.
